The DAO Hack

### 2019-01-05 paper/paper.tex
added what happened

\section{How was that possible?}

>>>>

In May 2016 when the DAO was launched on the ethereum blockchain it was funded with 12.7M ether. As one ether was worth about 10-12 Dollars at that time this corresponds to about 150 million dollars.

Soon after, on June 18 2016, an unknown party was able to drain the funds of the DAO by exploiting a security bug that was present in the function that is used to withdraw the ether. He was able to retrieve 3.5M ether which at that times would have been around 45 million dollars.

\subsection{How was that possible?}
